Expectations, Outcomes, and Challenges \\ of Modern Code Review

### 2013-01-08 sections/challenges.tex
Added figures and references to them

From interviews, no other code review challenge emerged as clearly as understanding the submitted change. Even though scheduling and time issues also appeared challenging, we could always trace them back to the first challenge—through the words of a tester: \quotation{understanding the code takes most of the reviewing time.} On the same note, in the code review comments we analyzed, the second most frequent category concerns understanding. This category includes clarification questions and doubts raised by the reviewers who want to grasp the rationale of the changes done on the code, and the corresponding clarification answers. This is also in line with the evidence delivered by Sutherland \& Venolia on the relevance of rationale articulation in reviews~\cite{sutherland2009can}.

Do understanding needs change with the expected outcome of code review? We included a question in the programmers' survey to know how much understanding they needed to achieve each of the motivations listed in \figref{XXX3}. The outcome of the question is summarized in \figref{XXX5}. The respondents could answer with a four values Likert's scale, by selecting the understanding of the change they felt was required to achieve the specific outcome. The most difficult task from the understanding perspective is \emph{finding defects}, immediately followed by \emph{alternative solutions}. Both clearly stand out from the other items. The gap in understanding needs between \emph{finding defects} and \emph{code improvement} seems to corroborate our hypothesis that the difference in the number of comments about these two items in review comments is mostly due to understanding issues. Thus, if managers and developers want code review to match their need for \emph{finding defects}, context and change understanding must be improved.

>>>>

\begin{figure}[t] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\columnwidth]{understanding.pdf}
   \vspace{-1.5em}
   \caption{Developers’ responses in surveys of the amount of code understanding for code review outcomes.}
   \label{fig:understanding}
   \vspace{-1.5em}
\end{figure}

From interviews, no other code review challenge emerged as clearly as understanding the submitted change. Even though scheduling and time issues also appeared challenging, we could always trace them back to the first challenge through the words of a tester: \quotation{understanding the code takes most of the reviewing time.} On the same note, in the code review comments we analyzed, the second most frequent category concerns understanding. This category includes clarification questions and doubts raised by the reviewers who want to grasp the rationale of the changes done on the code, and the corresponding clarification answers. This is also in line with the evidence delivered by Sutherland \& Venolia on the relevance of rationale articulation in reviews~\cite{sutherland2009can}.

Do understanding needs change with the expected outcome of code review? We included a question in the programmers' survey to know how much understanding they needed to achieve each of the motivations listed in \figref{fig:dev-motivations}. The outcome of the question is summarized in \figref{fig:understanding}. The respondents could answer with a four values Likert's scale, by selecting the understanding of the change they felt was required to achieve the specific outcome. The most difficult task from the understanding perspective is \emph{finding defects}, immediately followed by \emph{alternative solutions}. Both clearly stand out from the other items. The gap in understanding needs between \emph{finding defects} and \emph{code improvement} seems to corroborate our hypothesis that the difference in the number of comments about these two items in review comments is mostly due to understanding issues. Thus, if managers and developers want code review to match their need for \emph{finding defects}, context and change understanding must be improved.
